abxD01 Paper

### 2015-03-11 PAPER.Rmd
Add to discussion

Correlation analysis alone was insufficient in identifying all informative bacteria. Random forest modeling allowed us to identify several bacterial OTUs that did not have significant correlations with *C. difficile* yet improved model accuracy. *Turicibacter* and *Akkermansia*, for example, both had non-significant correlations with *C .difficile* yet were more important for model accuracy over OTUs with stronger correlations (*Figure 5BC*). While these bacteria may not have important direct effects on *C. difficile*, they may interact positively or negatively with bacteria that do have strong relationships with *C. difficile*. Modeling of the microbiome allows us to characterize *C. difficile* colonization in terms of a community, which is necessary to capture the complex relationships among its members. Few studies attempt to model the microbiome to predict disease or estimate health [Pamer, clostridium paper, psoriases, schubert].

@@

>>>>

@@

Modeling of the microbiome allows us to characterize *C. difficile* colonization in terms of a community, which is necessary to capture these complex relationships among its members. Correlation analysis alone was insufficient in identifying all informative bacteria. Random forest modeling allowed us to identify several bacterial OTUs that did not have significant correlations with *C. difficile* yet improved model accuracy. *Turicibacter* and *Akkermansia*, for example, both had non-significant correlations with *C .difficile* yet were more important for model accuracy over OTUs with stronger correlations (*Figure 5BC*). While these bacteria may not have important direct effects on *C. difficile*, they may interact positively or negatively with bacteria that do have strong relationships with *C. difficile*. Although the applications for microbiome modelling are diverse, given the microbiome's relationship to many aspects of human health and disease, there are currently few studies attempt to model the microbiome to predict disease or estimate health [Pamer, psoriases, schubert]. Microbiome modeling has been successfully applied to the prediction of psoriasis diagnosis, in which a microbiota signature defining subjects with and without psoriasis was discovered [Statnikov et al 2013]. In a time-series model of microbiome dynamics, the microbiota response to clindamycin or clindamycin followed by *C. difficile* challenge was predicted.

--------------
